---
title       : Tuna Atlas indicators
subtitle    : Quelques exemples de Plots
author      : Julien Barde
date        : September 21, 2015
job         : UMR MARBEC, IRD, Sète
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      #   
widgets     : [bootstrap, quiz]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
license     : by-nc-sa
github:
  user: juldebar
  repo: IRDTunaAtlas
logo        : mydeck/assets/img/logo_IRD.svg
knit        : slidify::knit2slides
ext_widgets : {rCharts: [libraries/nvd3]}
---
<img style="position: absolute; top: 0; right: 0; border: 0;" src="http://mdst-macroes.ird.fr/FAO_SWIO_Workshop/assets/img/logo_IRD.svg" width="250">
## Installation

- Installation du paquet GIT sur l'OS:
```{r install_github_repository, eval=FALSE}
git  clone https://github.com/juldebar/IRDTunaAtlas.git
```
- Créer un nouveau projet avec Git => clone 
- Compiler les sources du package dans R (répertoire à adapter):
```{r compil_package, message = F, eval=FALSE}
setwd("/home/tomcat7/IRDTunaAtlas/")
devtools::build()
install.packages("/home/tomcat7/IndicatorsForFisheries_0.2.tar.gz",
type="source", repo=NULL)
```

Si besoin remettre les codes du serveur Github (dans un terminal dans le répertoire du package):
```{r align_github, eval=FALSE}
git fetch --all
git reset --hard origin/master
```

---
<img style="position: absolute; top: 0; right: 0; border: 0;" src="http://mdst-macroes.ird.fr/documentation/databases/Sardara/logos/logo_sardara_cmyk_vector.svg" width="300">
## INDICATOR 1: WFS data access 
```{r indicator1, message = F}
require(IRDTunaAtlas)
df <- readData(connectionType="remote", dataType="WFS",
       url="http://mdst-macroes.ird.fr:8080/constellation/WS/wfs/tuna_atlas",
       layer="ns11:i1i2_mv", 
       ogcFilter='<ogc:Filter xmlns:ogc="http://www.opengis.net/ogc" xmlns:gml="http://www.opengis.net/gml"><ogc:PropertyIsEqualTo><ogc:PropertyName>species</ogc:PropertyName><ogc:Literal>YFT</ogc:Literal></ogc:PropertyIsEqualTo></ogc:Filter>',
       withSparql=FALSE)
indicator1 <- Atlas_i1_SpeciesByOcean_julien(df=df, yearAttributeName="year",
                                             oceanAttributeName="ocean",
                                             speciesAttributeName="species",
                                             valueAttributeName="value")
```

--
<img style="position: absolute; top: 0; right: 0; border: 0;" src="http://mdst-macroes.ird.fr/documentation/databases/Sardara/logos/logo_sardara_cmyk_vector.svg" width="300">
## INDICATOR 1: ggplot result
```{r i1_ggplot_result}
    plotRchartsNVD3 <- nPlot(value ~ year, group = 'ocean', data = aggData, type = 'stackedAreaChart', id = 'chart')
    plotRchartsNVD3$xAxis(axisLabel = 'Year')
    plotRchartsNVD3$yAxis(axisLabel = 'Catches')
    plotRchartsNVD3$chart(width = 800, height = 400, useInteractiveGuideline=TRUE)
    plotRchartsNVD3
    
```

print(indicator1) 

--
<img style="position: absolute; top: 0; right: 0; border: 0;" src="http://mdst-macroes.ird.fr/documentation/databases/Sardara/logos/logo_sardara_cmyk_vector.svg" width="300">
## INDICATOR 1: rCharts result example (see others)
<iframe src = 'http://mdst-macroes.ird.fr/tmp/SpeciesByOcean/I1_Thunnus_albacares_NVD3.html' onload="this.width=screen.width;this.height=screen.height;"></iframe>

---
<img style="position: absolute; top: 0; right: 0; border: 0;" src="http://mdst-macroes.ird.fr/documentation/databases/Sardara/logos/logo_sardara_cmyk_vector.svg" width="300">
## INDICATOR 2: WFS data access 
```{r indicator2, results = 'hide', tidy = F, message = F}
require(IRDTunaAtlas)
df <- readData(connectionType="remote", dataType="WFS",
       url="http://mdst-macroes.ird.fr:8080/constellation/WS/wfs/tuna_atlas",
       layer="ns11:i1i2_mv", 
       ogcFilter='<ogc:Filter xmlns:ogc="http://www.opengis.net/ogc" xmlns:gml="http://www.opengis.net/gml"><ogc:PropertyIsEqualTo><ogc:PropertyName>species</ogc:PropertyName><ogc:Literal>YFT</ogc:Literal></ogc:PropertyIsEqualTo></ogc:Filter>',withSparql=FALSE)
indicator2 <- Atlas_i2_SpeciesByGear_julien(df=df, 
                                 yearAttributeName="year", 
                                 gearTypeAttributeName="gear_type", 
                                 speciesAttributeName="species", 
                                 valueAttributeName="value")
```

---
<img style="position: absolute; top: 0; right: 0; border: 0;" src="http://mdst-macroes.ird.fr/documentation/databases/Sardara/logos/logo_sardara_cmyk_vector.svg" width="300">
## INDICATOR 2: ggplot result
```{r i2_ggplot_result}
require(rCharts)
indicator2
```

print(indicator2) 

---
<img style="position: absolute; top: 0; right: 0; border: 0;" src="http://mdst-macroes.ird.fr/documentation/databases/Sardara/logos/logo_sardara_cmyk_vector.svg" width="300">
## INDICATOR 2: rCharts result
<iframe src = 'http://mdst-macroes.ird.fr/tmp/SpeciesByGear/I2_Thunnus_albacaresNVD3.html' onload="this.width=screen.width;this.height=screen.height;"></iframe>

---
<img style="position: absolute; top: 0; right: 0; border: 0;" src="http://mdst-macroes.ird.fr/documentation/databases/Sardara/logos/logo_sardara_cmyk_vector.svg" width="300">
## INDICATOR 3: WFS data access 
```{r indicator3, results = 'hide', tidy = F, message = F}
require(IRDTunaAtlas)
df <- readData(connectionType="remote", dataType="WFS",
               url="http://mdst-macroes.ird.fr:8080/constellation/WS/wfs/tuna_atlas",
ogcFilter='<ogc:Filter xmlns:ogc="http://www.opengis.net/ogc" xmlns:gml="http://www.opengis.net/gml"><ogc:PropertyIsEqualTo><ogc:PropertyName>species</ogc:PropertyName><ogc:Literal>YFT</ogc:Literal></ogc:PropertyIsEqualTo><ogc:PropertyIsEqualTo><ogc:PropertyName>year</ogc:PropertyName><ogc:Literal>2005</ogc:Literal></ogc:PropertyIsEqualTo></ogc:Filter>',
               layer="ns11:i3_mv")
#build the I3 indicator
indicator3 <- Atlas_i3_SpeciesYearByGearMonth_julien(df=df, 
                                 yearAttributeName="year", 
                                 monthAttributeName="month",
                                 gearTypeAttributeName="gear_type", 
                                 speciesAttributeName="species", 
                                 valueAttributeName="value",
                                 meanPrev5YearsAttributeName="mean_prev_5_years",
                                 stddevPrev5YearsAttributeName="stddev_prev_5_years")
```

---
<img style="position: absolute; top: 0; right: 0; border: 0;" src="http://mdst-macroes.ird.fr/documentation/databases/Sardara/logos/logo_sardara_cmyk_vector.svg" width="300">
## INDICATOR 3: ggplot result 
```{r i3_ggplot_result, fig.align = 'center', fig.height = 6, fig.width = 6}
print(indicator3) 
```

---
<img style="position: absolute; top: 0; right: 0; border: 0;" src="http://mdst-macroes.ird.fr/documentation/databases/Sardara/logos/logo_sardara_cmyk_vector.svg" width="300">
## INDICATOR 3: rCharts result
<iframe src = 'http://mdst-macroes.ird.fr/tmp/SpeciesByYearByMonthByGear/I3_Thunnus_obesus_2000_bingo.html' onload="this.width=screen.width;this.height=screen.height;"></iframe>

---
<img style="position: absolute; top: 0; right: 0; border: 0;" src="http://mdst-macroes.ird.fr/documentation/databases/Sardara/logos/logo_sardara_cmyk_vector.svg" width="300">
## INDICATOR 4: WFS data access
```{r indicator4, results = 'hide', tidy = F, message = F}
library(IRDTunaAtlas)
df <- readData(connectionType="remote", dataType="WFS",
               url="http://mdst-macroes.ird.fr:8080/constellation/WS/wfs/tuna_atlas",
               layer="ns11:i4_mv", 
               ogcFilter='<ogc:Filter xmlns:ogc="http://www.opengis.net/ogc" xmlns:gml="http://www.opengis.net/gml"><ogc:And><ogc:PropertyIsEqualTo><ogc:PropertyName>species</ogc:PropertyName><ogc:Literal>YFT</ogc:Literal></ogc:PropertyIsEqualTo><ogc:PropertyIsLessThanOrEqualTo><ogc:PropertyName>year</ogc:PropertyName><ogc:Literal>2005</ogc:Literal></ogc:PropertyIsLessThanOrEqualTo><ogc:PropertyIsGreaterThanOrEqualTo><ogc:PropertyName>year</ogc:PropertyName><ogc:Literal>2000</ogc:Literal></ogc:PropertyIsGreaterThanOrEqualTo></ogc:And></ogc:Filter>')


#build the I4 indicator
indicator4 <- Atlas_i4_SpeciesMonthByOcean_julien(df=df, 
                                          oceanAttributeName="ocean", 
                                          yearAttributeName="year", 
                                          monthAttributeName="month",
                                          speciesAttributeName="species", 
                                          valueAttributeName="value")
```

---
<img style="position: absolute; top: 0; right: 0; border: 0;" src="http://mdst-macroes.ird.fr/documentation/databases/Sardara/logos/logo_sardara_cmyk_vector.svg" width="300">
## INDICATOR 4: ggplot result
```{r i4_ggplot_result, fig.align = 'center', fig.height = 10, fig.width = 10}
print(indicator4) 
```

no rCharts version for now

---
<img style="position: absolute; top: 0; right: 0; border: 0;" src="http://mdst-macroes.ird.fr/documentation/databases/Sardara/logos/logo_sardara_cmyk_vector.svg" width="300">
## INDICATOR 6: WFS data access
```{r indicator6, results = 'hide', tidy = F, message = F, cache.comments=TRUE,}
require(IRDTunaAtlas)
#fetch data from IRD WFS for indicator I6, with restriction on species="YFT" and year=2000
  df <- readData(connectionType="remote", dataType="WFS",
		       url="http://mdst-macroes.ird.fr:8080/constellation/WS/wfs/tuna_atlas",
		       layer="ns11:i6i7i8_mv", 
		       ogcFilter='<ogc:Filter xmlns:ogc="http://www.opengis.net/ogc" xmlns:gml="http://www.opengis.net/gml"><ogc:And><ogc:PropertyIsEqualTo><ogc:PropertyName>species</ogc:PropertyName><ogc:Literal>YFT</ogc:Literal></ogc:PropertyIsEqualTo><ogc:PropertyIsEqualTo><ogc:PropertyName>year</ogc:PropertyName><ogc:Literal>2000</ogc:Literal></ogc:PropertyIsEqualTo></ogc:And></ogc:Filter>',withSparql=FALSE)

	#build the I6 indicator
	indicator6 <- Atlas_i6_SpeciesMap_julien(df=df, 
		                      geomIdAttributeName="geom_id",
		                      yearAttributeName="year", 
		                      speciesAttributeName="species",                                         
		                      valueAttributeName="value")
```

---
<img style="position: absolute; top: 0; right: 0; border: 0;" src="http://mdst-macroes.ird.fr/documentation/databases/Sardara/logos/logo_sardara_cmyk_vector.svg" width="300">
## INDICATOR 6: ggplot result
```{r i6_ggplot_result, fig.align = 'center', fig.height = 6, fig.width = 6}
print(indicator6) 
```

---
<img style="position: absolute; top: 0; right: 0; border: 0;" src="http://mdst-macroes.ird.fr/documentation/databases/Sardara/logos/logo_sardara_cmyk_vector.svg" width="300">
## INDICATOR 6: netCDF / Thredds & WMS & Openlayers result
<iframe src = 'http://mdst-macroes.ird.fr:8080/thredds/godiva2/godiva2.html?server=http://mdst-macroes.ird.fr:8080/thredds/wms/macroes/world/indicators_i6i7i8/indicatorsi6i7i8_YFT_19501980.ncml#' onload="this.width=screen.width;this.height=screen.height;"></iframe>

---
<img style="position: absolute; top: 0; right: 0; border: 0;" src="http://mdst-macroes.ird.fr/documentation/databases/Sardara/logos/logo_sardara_cmyk_vector.svg" width="300">
## INDICATOR 7: WFS data access
```{r indicator7, results = 'hide', tidy = F, message = F}
library(IRDTunaAtlas)
#fetch data from IRD WFS for indicator I7, with restriction on species="YFT" and year=2000
df <- readData(connectionType="remote", dataType="WFS",
               url="http://mdst-macroes.ird.fr:8080/constellation/WS/wfs/tuna_atlas",
               layer="ns11:i6i7i8_mv", 
               ogcFilter='<ogc:Filter xmlns:ogc="http://www.opengis.net/ogc" xmlns:gml="http://www.opengis.net/gml"><ogc:And><ogc:PropertyIsEqualTo><ogc:PropertyName>species</ogc:PropertyName><ogc:Literal>YFT</ogc:Literal></ogc:PropertyIsEqualTo><ogc:PropertyIsEqualTo><ogc:PropertyName>year</ogc:PropertyName><ogc:Literal>2000</ogc:Literal></ogc:PropertyIsEqualTo></ogc:And></ogc:Filter>')

#build the I7 indicator
indicator7 <- Atlas_i7_SpeciesMapRelativeCatches(df=df, 
                              geomIdAttributeName="geom_id",
                              yearAttributeName="year", 
                              speciesAttributeName="species",                                         
                              valueAttributeName="value")
```

---
<img style="position: absolute; top: 0; right: 0; border: 0;" src="http://mdst-macroes.ird.fr/documentation/databases/Sardara/logos/logo_sardara_cmyk_vector.svg" width="300">
## INDICATOR 7: ggplot result
```{r i7_ggplot_result, fig.align = 'center', fig.height = 6, fig.width = 6}
print(indicator7) 
```
no rCharts version but Openlayers possible thourgh netCDF export and Thredds ncWMS

---
<img style="position: absolute; top: 0; right: 0; border: 0;" src="http://mdst-macroes.ird.fr/documentation/databases/Sardara/logos/logo_sardara_cmyk_vector.svg" width="300">
## INDICATOR 8: WFS data access
```{r indicator8, results = 'hide', tidy = F, message = F}
library(IRDTunaAtlas)
#fetch data from IRD WFS for indicator I8, with restriction on species="YFT" and year=2000
df <- readData(connectionType="remote", dataType="WFS",
               url="http://mdst-macroes.ird.fr:8080/constellation/WS/wfs/tuna_atlas",
               layer="ns11:i6i7i8_mv", 
               ogcFilter='<ogc:Filter xmlns:ogc="http://www.opengis.net/ogc" xmlns:gml="http://www.opengis.net/gml"><ogc:And><ogc:PropertyIsEqualTo><ogc:PropertyName>species</ogc:PropertyName><ogc:Literal>YFT</ogc:Literal></ogc:PropertyIsEqualTo><ogc:PropertyIsEqualTo><ogc:PropertyName>year</ogc:PropertyName><ogc:Literal>2000</ogc:Literal></ogc:PropertyIsEqualTo></ogc:And></ogc:Filter>')

#build the I8 indicator with targeted species = "YFT"
indicator8 <- Atlas_i8_SpeciesMapRelativeCatchesOtherSpecies(df=df, 
                                             targetedSpecies="YFT",
                                             geomIdAttributeName="geom_id",
                                             yearAttributeName="year", 
                                             speciesAttributeName="species",                                         
                                             valueAttributeName="value")
```

---
<img style="position: absolute; top: 0; right: 0; border: 0;" src="http://mdst-macroes.ird.fr/documentation/databases/Sardara/logos/logo_sardara_cmyk_vector.svg" width="300">
## INDICATOR 8: ggplot result
```{r i8_ggplot_result, fig.align = 'center', fig.height = 6, fig.width = 6}
print(indicator8) 
```

---
<img style="position: absolute; top: 0; right: 0; border: 0;" src="http://mdst-macroes.ird.fr/documentation/databases/Sardara/logos/logo_sardara_cmyk_vector.svg" width="300">
## INDICATOR 9: WFS data access
```{r indicator9, results = 'hide', tidy = F, message = F}
require(IRDTunaAtlas)
df <- readData(connectionType="remote", dataType="WFS",
               url="http://mdst-macroes.ird.fr:8080/constellation/WS/wfs/tuna_atlas",
               layer="ns11:i9i10_mv", 
               ogcFilter='<ogc:Filter xmlns:ogc="http://www.opengis.net/ogc" xmlns:gml="http://www.opengis.net/gml"><ogc:And><ogc:PropertyIsEqualTo><ogc:PropertyName>species</ogc:PropertyName><ogc:Literal>YFT</ogc:Literal></ogc:PropertyIsEqualTo><ogc:PropertyIsEqualTo><ogc:PropertyName>year</ogc:PropertyName><ogc:Literal>2000</ogc:Literal></ogc:PropertyIsEqualTo></ogc:And></ogc:Filter>')

#build the I9 indicator
indicator9 <- Atlas_i9_RelativeSizeFrequenciesBySchoolType_julien(df=df, 
                                                         yearAttributeName="year", 
                                                         speciesAttributeName="species", 
                                                         schoolAttributeName="school",
                                                         sizeClassLowerBoundAttributeName="class_low",
                                                         sizeClassUpperBoundAttributeName="class_up",
                                                         fishCountAttributeName="fish_count")
```

---
<img style="position: absolute; top: 0; right: 0; border: 0;" src="http://mdst-macroes.ird.fr/documentation/databases/Sardara/logos/logo_sardara_cmyk_vector.svg" width="300">
## INDICATOR 9: ggplot result
```{r i9_ggplot_result, fig.align = 'center', fig.height = 6, fig.width = 6}
print(indicator9) 
```

---
<img style="position: absolute; top: 0; right: 0; border: 0;" src="http://mdst-macroes.ird.fr/documentation/databases/Sardara/logos/logo_sardara_cmyk_vector.svg" width="300">
## INDICATOR 9: rCharts result
<iframe src = 'http://mdst-macroes.ird.fr/tmp/RelativeSizeFrequenciesBySchoolType/I9__Thunnus_obesus_2005_-_2005bis.html' onload="this.width=screen.width;this.height=screen.height;"></iframe>

---
## INDICATOR 10: WFS data access
```{r indicator10, results = 'hide', tidy = F, message = F}
library(IRDTunaAtlas)
#fetch data from IRD WFS for indicators I10, with restriction on species="YFT" and year >= 1980 and year <= 2005
df <- readData(connectionType="remote", dataType="WFS",
               url="http://mdst-macroes.ird.fr:8080/constellation/WS/wfs/tuna_atlas",
               layer="ns11:i9i10_mv", 
               ogcFilter='<ogc:Filter xmlns:ogc="http://www.opengis.net/ogc" xmlns:gml="http://www.opengis.net/gml"><ogc:And><ogc:PropertyIsEqualTo><ogc:PropertyName>species</ogc:PropertyName><ogc:Literal>YFT</ogc:Literal></ogc:PropertyIsEqualTo><ogc:PropertyIsLessThanOrEqualTo><ogc:PropertyName>year</ogc:PropertyName><ogc:Literal>2005</ogc:Literal></ogc:PropertyIsLessThanOrEqualTo><ogc:PropertyIsGreaterThanOrEqualTo><ogc:PropertyName>year</ogc:PropertyName><ogc:Literal>1980</ogc:Literal></ogc:PropertyIsGreaterThanOrEqualTo></ogc:And></ogc:Filter>')

#build the I10 indicator
indicator10 <- Atlas_i10_RelativeSizeFrequenciesByDecade(df=df, 
                                                       temporalAgg=10,
                                                       yearAttributeName="year", 
                                                       speciesAttributeName="species", 
                                                       sizeClassLowerBoundAttributeName="class_low",
                                                       sizeClassUpperBoundAttributeName="class_up",
                                                       fishCountAttributeName="fish_count")
```

---
<img style="position: absolute; top: 0; right: 0; border: 0;" src="http://mdst-macroes.ird.fr/documentation/databases/Sardara/logos/logo_sardara_cmyk_vector.svg" width="300">
## INDICATOR 10: ggpot result
```{r i10_ggplot_result, fig.align = 'center', fig.height = 6, fig.width = 6}
print(indicator10) 
```

---
<img style="position: absolute; top: 0; right: 0; border: 0;" src="http://mdst-macroes.ird.fr/documentation/databases/Sardara/logos/logo_sardara_cmyk_vector.svg" width="300">
## INDICATOR 11: WFS data access
```{r indicator11, results = 'hide', tidy = F, message = F}
library(IRDTunaAtlas)
#fetch data from IRD WFS for indicators I11 with restriction on species="YFT" and year=2000
df <- readData(connectionType="remote", dataType="WFS",
               url="http://mdst-macroes.ird.fr:8080/constellation/WS/wfs/tuna_atlas",
               layer="ns11:i6i7i8_mv", 
               ogcFilter='<ogc:Filter xmlns:ogc="http://www.opengis.net/ogc" xmlns:gml="http://www.opengis.net/gml"><ogc:And><ogc:PropertyIsEqualTo><ogc:PropertyName>species</ogc:PropertyName><ogc:Literal>YFT</ogc:Literal></ogc:PropertyIsEqualTo><ogc:PropertyIsEqualTo><ogc:PropertyName>year</ogc:PropertyName><ogc:Literal>2000</ogc:Literal></ogc:PropertyIsEqualTo></ogc:And></ogc:Filter>')

#build the I11 indicator
indicator11 <- Atlas_i11_CatchesByCountry(df=df, 
                                     geomIdAttributeName="geom_id",
                                     countryAttributeName="country", 
                                     speciesAttributeName="species",                                         
                                     valueAttributeName="value")
```

---
<img style="position: absolute; top: 0; right: 0; border: 0;" src="http://mdst-macroes.ird.fr/documentation/databases/Sardara/logos/logo_sardara_cmyk_vector.svg" width="300">
## INDICATOR 11: ggplot result
```{r i11_result, fig.align = 'center', fig.height = 6, fig.width = 6}
print(indicator11) 
```

---
## NVD3 Plots using rCharts

This is a short tutorial on how to use NVD3 with rCharts. The source for this tutorial can be found [here](https://gist.github.com/ramnathv/8070363#file-example6-rmd)

```{r setup, tidy = F, cache = F, echo = F}
library(rCharts)
options(
  rcharts.mode = 'iframesrc', 
  rcharts.cdn = TRUE,
  RCHART_WIDTH = 700,
  RCHART_HEIGHT = 400
)
library(knitr)
opts_chunk$set(tidy = F, results = 'asis', comment = NA)
```
---
## test rCharts
```{r rcharts, fig.align = 'center', fig.height = 6, fig.width = 6}
require(rCharts)
haireye = as.data.frame(HairEyeColor)
n1 <- nPlot(Freq ~ Hair, 
  group = 'Eye',
  data = subset(haireye, Sex == 'Male'),
  type = 'multiBarChart'
)
n1$print('chart1')
```

---
### Scatter Chart

```{r}
p1 <- nPlot(mpg ~ wt, group = 'cyl', data = mtcars, type = 'scatterChart')
p1$xAxis(axisLabel = 'Weight')
p1
```
